### 2023-02-17 definitions.tex
Thinking Resilience (not bounded resilience but resilience itself) is decidable for WSTS with post* effectiveness. Have written a proof, needs to re-read. Will keep trying to see if Bounded is too or could be proven to be undecidable

>>>>

\begin{theorem}
{\sc Resilience} is decidable for (not necessarily strong) WSTS with effective $\uparrow$ $\post^*$ basis.
\end{theorem}

\begin{proof}
Let $B_p$ be a basis of $\uparrow \post^*(s)$, $B_I$ a basis of $I$
and $J$ decidable downward-closed.
By applying Lemma~\ref{Lemma intersection} twice, we obtain

$$ post^*(s) \cap J \subseteq \pred^*(I) \equiv B_p \cap J \subseteq \pred^*(I)$$

Since $B_p$ is finite and $J$ is decidable, we can directly compute $ B_p \cap J$.
% For every element of $ B_p \cap J$, checking that it is in $\pred^*(I)$ is the same as checking coverability of I, and thus decidable.
We can compute a basis of $\pred^*(I)$ from $B_I$, and hence check that $B_p \cap J \setminus \pred^*(I) = \emptyset$. 
\end{proof}

% In the proof of Thm. 1, it was crucial that we have strong compatibility. This approach does not work
% for WSTSs in general. We loose precision when we only demand compatibility. Thus, we conjecture
% that both resilience problems are undecidable for WSTSs in general, but this question remains still open.
%
% Well, maybe their version of resilience but resilience with * seems fine.
%
